---
title: "Week 3 Assignment"
author: "HK Kim"
date: "December 27, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

### Peer-graded assignment: R Markdown Presentation & Plotly

## Goal
Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly.

## Diamonds dataset

- "diamonds" dataset will be used in this demo.
- Dataset looks like below:

```{r diamonds, echo = FALSE, warning=FALSE}
library(plotly)
head(diamonds)
```

## Plotting Price against Carat
Since diamonds dataset is quite large, we take random 2000 samples and plot price against carat. Each datapoint is color-coded by its color type.

```{r, echo=FALSE, warning=FALSE, message=FALSE}

diamonds2 <- diamonds[sample(nrow(diamonds), 2000),]
plot_ly(x = diamonds2$carat, y=diamonds2$price, mode = "markers", color = diamonds2$color)

```

